14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-20 rules/rules19.tex
Rules: Competition-wide recognitions (still not finalized).

  \item {\bf Competition-Wide Recognitions.} \todo{}

@@

\subsection{Other Recognitions \todo{Update}}

>>>>

  \item {\bf Competition-Wide Recognitions.}
    This year, we will replace the previous notion of competition-wide scoring
    as introduced for the Main Track in 2014 (and improved over the years)
    with recognitions for all tracks that do not directly compare divisions.
    {\color{red} Details to be announced.}
    \rationale{Competition-wide scoring was introduced as a metric to
    compare solver performance across all divisions. By definition, this metric
    is biased towards solvers that enter a large number of divisions.}

@@

\subsection{Competition-Wide Recognitions}

{\color{red} Details to be announced.}

\subsection{Other Recognitions}
